---
title: "YunMai_hw_7_8"
author: "Yun Mai"
date: "March 24, 2018"
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Chapter 8 Modeling Using Graph Theory

### 8.4 Using Graph Models to Solve Problems

Page 331: #1
1. Find a shortest path from node a to node j in the graph in Figure 8.33 with edge weights shown on the graph.

**Solution**
```{r}
suppressMessages(suppressWarnings(library(igraph)))

edgelist <- rbind( c('a','b',2), c('a','c',4),c('b','e',7),c('b','d',2),c('c','f',2), c('c','e',4), c('d','g',2), c('e','i',3), c('e','h',2), c('e','g',1), c('f','i',6), c('h','j',4), c('i','j',2), c('g','j',8))

colnames(edgelist) <- c("from", "to", "capacity")
edgelist <- as.data.frame(edgelist)

g <- graph_from_edgelist(as.matrix(edgelist[,c('from','to')]))

E(g)$capacity <- edgelist$capacity
edgelist$capacity
E(g)$capacity

plot(g, edge.label = E(g)$capacity)

g1 <- graph_from_data_frame(as.matrix(edgelist))

get.shortest.paths(g1, from=V(g1)[1], to=V(g1)[10], mode = c("all"), weights = edgelist$capacity)

distMatrix <- shortest.paths(g1, v=V(g1), mode = c("all"),
      weights = edgelist$capacity)
distMatrix["a", "j"]

```

So the shortest path from node a to node j is 12. This result is consistent to what I got by using the Dijkstra's Shortest-Path Algorithm.

Page 331: #3

3. Use our maximum-flow algorithm to find the maximum flow from s to t in the graph of Figure 8.31.

Maximum-Flow Algorithm:

**Input** A directed graph G =V(G) A(G)// with with a source vertex s and a sink vertex t and a finite flow capacity uij for each arc $ij 2 A(G)$. Let $u_{ij} = 0$ for all $ij \in A(G)$.

**Output** The maximum flow from s to t in G.

**Step 0** Set the current ow to zero: fc 0.

**Step 1** Find a directed path from s to t in the current graph. If there is no such path, stop. The maximum flow from s to t in G is fc.

**Step 2** Compute umin, the minimum capacity in the current graph of all the arcs in the directed path.

**Step 3** For each arc ij in the directed path, update the residual capacity in the current graph: $u_{ij} \leftarrow u_{ij}- u_min $. Also update "reverse"" arc capacities: $u_{ji} \leftarrow u_{ji}+ u_min$.

**Step 4** Set $f_c \leftarrow f_c + u_min$ and return to Step 1.

```{r}
#plot Figure 8.31
edgelist <- rbind( c('s','x1'),c('x1','y1'),c('y1','t'), 
                   c('s','x1'),c('x1','y2'),c('y2','t'),
                   c('s','x1'),c('x1','y4'),c('y4','t'),
                   c('s','x1'),c('x1','y5'),c('y5','t'),
                   c('s','x2'),c('x2','y3'),c('y3','t'),
                   c('s','x2'),c('x2','y6'),c('y6','t'),
                   c('s','x3'),c('x3','y3'),c('y3','t'),
                   c('s','x4'),c('x4','y1'),c('y1','t'),
                   c('s','x4'),c('x4','y3'),c('y3','t'))

colnames(edgelist) <- c("from", "to")
edgelist <- as.data.frame(edgelist)

g <- graph_from_edgelist(as.matrix(edgelist[,c('from','to')]))

V(g)$x <- c(1,2,3,4,3,3,3,2,3,3,2,2)
V(g)$y <- c(4,6,6,4,5,3,2,4.5,4,1,3.5,1)
V(g)$color <- c('red', 'steelblue', 'green', 'pink', 'green', 'green', 'green','steelblue', 'green','green','steelblue','steelblue')
plot(g)

```




```{r}
max_flow(g, source=V(g)[1], target=V(g)[4])

```

The maximum flow from s to t in the graph of Figure 8.31 is 9.

## Chapter 9. Modeling With Decision Theory

### 9.1 Probability and Expected Value

Page 347: #4

4. We have engaged in a business venture. Assume the probability of success is
P(s)= 2/5; further assume that if we are successful we make $55,000, and if we
are unsuccessful we lose $1750. Find the expected value of the business venture.

$E(value) = P(s)\times 55000 + (1-P(s))\times 1750$

```{r}
Ps <- 2/5
(E_v <- Ps* 55000 + (1-Ps)* 1750)

```
 The expected value of the business venture is $23,050.

### 9.3 Sequential Decisions and Conditional Probabilities
Page 364: #3

3. A big private oil company must decide whether to drill in the Gulf of Mexico. It costs
\$1 million to drill, and if oil is found its value is estimated at \$6 million. At present,
the oil company believes that there is a 45% chance that oil is present. Before drilling
begins, the big private oil company can hire a geologist for $100,000 to obtain samples
and test for oil. There is only about a 60% chance that the geologist will issue a
favorable report. Given that the geologist does issue a favorable report, there is an
85% chance that there is oil. Given an unfavorable report, there is a 22% chance that
there is oil. Determine what the big private oil company should do.

```{r}
library(data.tree)

oil <- Node$new("oil campany")
  geologist_research <- oil$AddChild("geologist_research")
  favorable_report <- geologist_research$AddChild("Favorable_report")
    true1 <- favorable_report$AddChild("True")
    false1 <- favorable_report$AddChild("False")
  unfavorable_report <- geologist_research$AddChild("Unfavorable_report")
    true2 <- unfavorable_report$AddChild("True")
    false2 <- unfavorable_report$AddChild("False")
  no_geologist_research <- oil$AddChild("No_geologist_research")
    true3 <- no_geologist_research$AddChild("True")
    false3 <- no_geologist_research$AddChild("False")


favorable_report$p <- 0.6
true1$p <- 0.85
false1$p <- 0.15
unfavorable_report$p  <- 0.4
true2$p <- 0.22
false2$p <- 0.78
true2$p <- 0.45
false2$p <- 0.55

true1$cost <- 10^6*0.6*0.85
false1$cost <- 10^6*0.6*0.15
true2$cost <- 10^6*0.4*0.22
false2$cost <- 10^6*0.4*0.78
true3$cost <- 10^6*0.45
false3$cost <- 10^6*0.55

true1$profit <- 6*10^6*0.6*0.85
true2$profit <- 6*10^6*0.4*0.22
true3$profit <- 6*10^6*0.45

print(oil,"p","cost","profit")

```

```{r}
plot(oil)
```

```{r}
(E_pro <- ((0.6*0.85)+(0.4*0.22)+0.45)*6*10^6-10^6*2-10^5)
```

The expected profit of having the geolotist to investigate and drilling in the Gulf of Mexico will be \$4,188,000. If \$4,188,000 is acceptable, the big private oil company should go ahead to drill in the Gulf of Mexico.

 
