---
title: "YunMai_hw9_10"
author: "Yun Mai"
date: "April 10, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(kableExtra)))
suppressMessages(suppressWarnings(library(formattable)))
suppressMessages(suppressWarnings(library(dplyr)))

```

Page 385: #1 a, #1 c
Page 404: #2 a
Page 413: #3
Page 420: #1
Page 428: #3
Page 440: #2
Page 454: #3
    
    
Page 469: #3
Page 478: #6
Page 481: #1
Page 522: #21 and #22


Page 404: #2 a

2. For problems a-g build a linear programming model for each player's decisions and
solve it both geometrically and algebraically. Assume the row player is maximizing his
payoffs which are shown in the matrices below.

```{r,echo-F}
a <- data.frame('name'=rep('Rose',2),'strategy'=c('R1','R2'),'C1'=c(10,5),'C2'=c(10,0))
kable(a, "html", align = "c") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1) %>% 
  add_header_above(c(" "," ", "Colin" = 2))

```

Let

A: average payoffs
x: Portion of the time to play C1 strategy
1- x: Portion of the time to play C2 strategy
 
If Colin plays a pure C1 strategy, the expected value is

EV(C1) =  10x+5(1-x)

Similarly, if Colin plays C2 strategy, the expected value is

EV(C2) =  10x


The objective expression:
maximize A

The optimization problem for Rose:


```{r}

```
