---
title: "YunMai_hw9_10"
author: "Yun Mai"
date: "April 10, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(kableExtra)))
suppressMessages(suppressWarnings(library(formattable)))
suppressMessages(suppressWarnings(library(dplyr)))

```

Choose 2 problems from the following list:
Page 385: #1 a, #1 c
Page 404: #2 a
Page 413: #3
Page 420: #1
Page 428: #3
Page 440: #2
Page 454: #3
    
Choose 2 problems from the following list:
Page 469: #3
Page 478: #6
Page 481: #1
Page 522: #21 and #22

# Chapter 10: Game theory

## 10.2 Total Conflict as a Linear Program Model: Pure and Mix strategy

Page 404: #2 a

2. For problems a-g build a linear programming model for each player's decisions and solve it both geometrically and algebraically. Assume the row player is maximizing his payoffs which are shown in the matrices below 

```{r,echo-F}
a <- data.frame('name'=rep('Rose',2),'strategy'=c('R1','R2'),'C1'=c(10,5),'C2'=c(10,0))
kable(a, "html", align = "c") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1) %>% 
  add_header_above(c(" "," ", "Colin" = 2))

```

**Solution**

Let

S: average payoffs

x: Portion of the time to play R1 strategy

1- x: Portion of the time to play R2 strategy
 
If Colin plays a pure C1 strategy, the expected value is

EV(C1) =  10x+5(1-x)

Similarly, if Colin plays C2 strategy, the expected value is

EV(C2) =  10x


The objective expression:

maximize S

Constraints

S \leq 10x+5(1-x)

S \leq 10x 

0  \leq x  \leq 1

These inequations could be rewritten as follows:

S - 5x <=  5

S - 10x <=0

x <= 1

x >= 0

The constraints coule be write as:

$$
\begin{equation}
\begin{bmatrix}
    1       & -5  \\
    1       & -10
\end{bmatrix}
\begin{bmatrix}
    S \\
    x
\end{bmatrix}
=
\begin{bmatrix}
    5  \\
    0
\end{bmatrix}
\end{equation}
$$
let: 
$$
\begin{equation}
{f} = 
\begin{pmatrix}
  1   \\
  0
  \end{pmatrix}
\end{equation}
$$
and
$$
\begin{equation}
{x} = \begin{pmatrix}
  S   \\
  x
  \end{pmatrix}
\end{equation}
$$

The objective function:$max \ f^Tx$

The constraints: Ax <= c  

```{r}
suppressMessages(suppressWarnings(library(linprog)))  

# form c vector (f in object fucction)
cvec <- c(1, 0)

# form b vector (c in constraints expression)
bvec <- c(5,0) 

# form matrix A
A <- matrix(c(1,1,-5,-10),nrow=2,byrow=F)

res <- solveLP(cvec,bvec,A,maximum=TRUE)
res 
```

**The maximum payoffs for the row player is 10.**

Or we can solive the linear programming by the interior point method and graphically

```{r}
suppressMessages(suppressWarnings(library(intpoint)))
t <- 1
c <- t(cvec)
bm = c(5,0)
m = A
interior_point(t, c, bm , m, e = 1e-04, a1 = 1, a2 = 0.97)
```

** The result is the same: the maximum payoffs for the row player is 10.**

## 10.3 Desition Theory Revisits: Game Theory Against Nature

Page 413: #3

3. We are considering three alternatives A, B, or C or a mix of the three alternatives under uncertain conditions of the economy. The payoff matrix is as follows:

```{r,desion theory, echo-F}
tbl.2<- data.frame('Alternative'=c('A','B','C'),'No.1'=c(3000,1000,4500),'No.2'=c(4500,9000,4000),'No.3'=c(6000,2000,3500))
kable(tbl.2, "html", align = "c") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1) %>% 
  add_header_above(c(" ", "Condistions" = 3))

```

Set up and solve both the investor's and the economy's game.

**Solution**

V: Net profit in hundreds of thousands of dollars
x1: Portion of the time that the investor should play A
X2: Portion of the time that the investor should play B
1-x1-x2: Portion of the time that the investor should play C

objective function:

Maximize V

constraints:

$V <= 3000 \times x1+4500\times X2+6000\times (1-X1-X2)  Economy condition A$
$V <= 1000 \times x1+9000\times X2+2000\times (1-X1-X2)  Economy condition B$
$V <= 4500 \time sx1+4000\times X2+3500\times (1-X1-X2)  Economy condition C$
$x1 \leqslant 1$
$x1 \geqslant 0$
$x2 \leqslant 1$
$x2 \geqslant 0$

These inequations could be rewritten as follows:

S - 5x <=  5

S - 10x <=0

x <= 1

x >= 0

The constraints coule be write as:

$$
\begin{equation}
\begin{bmatrix}
    1   & 3000   & 1500  \\
    1   & -1000   & 7000  \\
    1   & 1000   & 500
\end{bmatrix}
\begin{bmatrix}
    V \\
    x1 \\
    x2
\end{bmatrix}
=
\begin{bmatrix}
    6000  \\
    2000  \\
    3500
\end{bmatrix}
\end{equation}
$$
let: 
$$
\begin{equation}
{f} = 
\begin{pmatrix}
  1   \\
  0   \\
  0
  \end{pmatrix}
\end{equation}
$$
and
$$
\begin{equation}
{x} = \begin{pmatrix}
  V   \\
  x1   \\
  x2
  \end{pmatrix}
\end{equation}
$$

The objective function:$max \ f^Tx$

The constraints: Ax <= c  

```{r}
#suppressMessages(suppressWarnings(library(linprog)))  

# form c vector (f in object fucction)
cvec <- c(1, 0,0)

# form b vector (c in constraints expression)
bvec <- c(6000,2000,3500) 

# form matrix A
A <- matrix(c(1,1,1,3000,1000,-1000,1500,-7000,-500),nrow=3,byrow=F)

res <- solveLP(cvec,bvec,A,maximum=TRUE)
res 
```

The geometric solution:
```{r}
suppressMessages(suppressWarnings(library(intpoint)))
t <- 1
c <- t(cvec)
bm = c(6000,2000,3500)
m = A
interior_point(t, c, bm , m, e = 1e-04, a1 = 1, a2 = 0.97)
```

The solution as x1=0.44,x2=0.36,V=$4125, giving the strategy for the investor as 44% A, 36% B and 20% C. Thus, if the investor plays a mixed strategy of 44% A, 36% B and 20% C
its net profit will be \$4125 regardless of whether the economy is in condition 1,2 or 3 or any mix of the condistions. At this point, theinvestor has a conservative strategy thatguarantees \$4125. 

**Economy's game:**

V: Net profit in hundreds of thousands of dollars
y1: Portion of the time that the economy in condition No.1
y2: Portion of the time that the economy in condition No.2
1-x1-x2: Portion of the time that the economy in condition No.3

objective function:

Maximize V

constraints:

$V <= 3000 \times x1+1000\times X2+4500\times (1-X1-X2)  Economy condition A$
$V <= 4500 \times x1+9000\times X2+4000\times (1-X1-X2)  Economy condition B$
$V <= 6000 \time sx1+2000\times X2+3500\times (1-X1-X2)  Economy condition C$
$y1 \leqslant 1$
$y1 \geqslant 0$
$y2 \leqslant 1$
$y2 \geqslant 0$

These inequations could be rewritten as follows:

S - 5x <=  5

S - 10x <=0

x <= 1

x >= 0

The constraints coule be write as:

$$
\begin{equation}
\begin{bmatrix}
    1   & 1500   & 3500  \\
    1   & -500   & -5000  \\
    1   & -2500   & 1500
\end{bmatrix}
\begin{bmatrix}
    V \\
    x1 \\
    x2
\end{bmatrix}
=
\begin{bmatrix}
    4500  \\
    4000  \\
    3500
\end{bmatrix}
\end{equation}
$$
let: 
$$
\begin{equation}
{f} = 
\begin{pmatrix}
  1   \\
  0   \\
  0
  \end{pmatrix}
\end{equation}
$$
and
$$
\begin{equation}
{x} = \begin{pmatrix}
  v   \\
  x1   \\
  x2
  \end{pmatrix}
\end{equation}
$$

The objective function:$max \ f^Tx$

The constraints: Ax <= c  

```{r}
#suppressMessages(suppressWarnings(library(linprog)))  

# form c vector (f in object fucction)
cvec <- c(1, 0,0)

# form b vector (c in constraints expression)
bvec <- c(4500,4000,3500) 

# form matrix A
A <- matrix(c(1,1,1,1500,-500,-2500,3500,-5000,1500),nrow=3,byrow=F)

res <- solveLP(cvec,bvec,A,maximum=TRUE)
res 
```

The geometric solution:
```{r}
suppressMessages(suppressWarnings(library(intpoint)))
t <- 0
c <- t(cvec)
bm = c(4500,4000,3500)
m = A
interior_point(t, c, bm , m, e = 1e-04, a1 = 1, a2 = 0.97)
```

Thr solution is economy plays 25% condition No.1, 0% condition No.2 and 75% condition No.3. To minimize profit is \$4125. No matter in what economy condition, could limit the investor's profit to \$4125.

## Chapter 11 

### 11.1 Population Growth

Page 469: #3

3. The following data were obtained for the growth of a sheep population introduced into a new environment on the island of Tasmania (adapted from J. Davidson, ``On the Growth of the Sheep Population in Tasmania,'' Trans. R. Soc. S. Australia 62(1938): 342-346).

```{r,population table, echo=F}
tb3 <- data.frame('t (year)'=c(1814, 1824, 1834, 1844, 1854, 1864),'P(t)' =c(125, 275, 830, 1200, 1750 ,1650))
kable(t(tb3))

```

a. Make an estimate of M by graphing P(t).

b. Plot lnP=[P/(M-P)]against t . If a logistic curve seems reasonable, estimate rM
and t*.

**Solution**
```{r}
t <- c(1814, 1824, 1834, 1844, 1854, 1864)
p <- c(125, 275, 830, 1200, 1750, 1650)

ggplot(data.frame(x=t,y=p),aes(x=x,y=y, fill = p)) + 
  geom_line() +
  geom_point() + 
  ggtitle("Sheep Population Growth") + 
  theme(plot.title = element_text(lineheight=.8, face="bold"))+
  xlab("Years")+
  ylab("Population")

```


The sheep population appears to reach a maximum level, and the last data point suggests that the data never exceeded 1750. I estimate M = 1750.

Then plot Years elapsed and Change p(t+1) - p(t)

```{r}
yearlapsed<- t-t[1]
p_changes<-0
for (i in 1:length(p)-1) {
  p_changes<- c(p_changes, p[i+1] -p[i]) 
  }
p_changes
yearlapsed

ggplot(data.frame(x=yearlapsed,y=p_changes),aes(x=x,y=y, fill = p_changes)) + 
  geom_line() +
  geom_point() + 
  ggtitle("Sheep Population Growth Change") + 
  theme(plot.title = element_text(lineheight=.8, face="bold"))+
  xlab("Elapsed Years")+
  ylab("Growth Change")

```

The plot suggests that the logistic curve is reasonable. Then estimate rM and t???.

```{r}
M <- 1800

#ln [P/ M - P]
ln_pMp <- log(p/(M-p))

suppressMessages(suppressWarnings(library(Laurae)))

# plot ln [P/ M - P] versus t
ggplot(data.frame(x=t,y=ln_pMp),aes(x=x,y=y, fill = ln_pMp)) + 
  geom_line() +
  geom_point() + 
  stat_smooth(method="lm")+
  stat_smooth_func(geom="text",method="lm",hjust=0,parse=TRUE)+
  ggtitle("ln [P/ M - P] versus t") + 
  theme(plot.title = element_text(lineheight=.8, face="bold"))+
  xlab("Years (t)")+
  ylab("ln [P/ M - P]")

```


The above graph does approximate to a straight line. Thus we accept the assumptions of logistic growth for the sheep population. rM = 0.119.

Then estimate the slope (rM) of the graph.
```{r}
rM <- lm(ln_pMp ~ t)
(rM <- rM$coefficients["t"])
```

Then estimate t* with the fomula as follows:

$t*=t_0 -\frac{1}{rM}+\frac{P_0}{M-P_0}$

```{r}
(t_star <- t[1] - (1/rM)*log(p[1]/(M-p[1])))
```

$P(t)= \frac{M}{1+e^{-rM(t-t*)}}$

```{r}
#p_t <- M/(1+exp(rM*t_star)*exp(-rM*t))
exp(rM*t_star)
```

$P(t)= \frac{1800}{1+6.433129^94 \times e^{(0.1189136 \times t)}}$

Let validate:

```{r}
t1 <- 1814
(p_t1 <- M/(1+exp(rM*t_star)*exp(-rM*t1)))
t2 <- 1824
(p_t2 <- M/(1+exp(rM*t_star)*exp(-rM*t2)))
t3 <- 1836
(p_t3 <- M/(1+exp(rM*t_star)*exp(-rM*t3)))

```

when t = 1814, p = 125 which is the same to the real data. 

when t = 1824,p = 355 which i higher than the real population 275.

when t = t* = 1835.825  = 1836, p = 910 which is close to p = M/2 = 1800/2= 900. 

In general, the logistical model roughly agrees with the population.


```{r}
(t_star <- t[1] - (1/rM)*log(p[1]/(M-p[1])))
```

### 11.7 Linear Equations

Page 522: #21
 
21. Oxygen flows through one tube into a liter flask falled with air, and the mixture of oxygen and air (considered well stirred) escapes through another tube. Assuming that
air contains 21% oxygen, what percentage of oxygen will the flask contain after 5 L
have passed through the intake tube?

**Solution**

the problem is 'proportion of oxygen' vs 'volume passed through'.

If P(v) is the proportion of Oxygen when a volume v has passed through, then the initial condition is when v=0, P=0.21.

The differential equation would be: dP = dv - dPv x 1, therefore, dP/dv = 1-P, when if an extra dv of oxygen pass into the flask, then an amount dPv comes out. 

The Deferential Equation: dP/dv = 1-P.

The initial condition is: P(0) = 0.21

```{r}
derivs <- function( r,y, parms)
  list(r-y)

suppressMessages(suppressWarnings(library(deSolve)))

yini <- 0.21
volums <- seq(from = 0, to = 5, by = 0.2)
(out <- ode(y = yini, times = volums, func = derivs, parms = NULL))
```

Therefore, the precentage of oxygen that flask will contain after 5 L is 4.0081531 Liters. 
 
 
